Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-06-02 semantic-nd/article.tex
Fixed citing style.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novelty Detection}
\label{sec:novelty-detection}
% Introduce novelty detection
Novelty detection deals with detecting that a data sample belongs to a class
originated by a distribution other than the ones the system knows about \citep{markou2003novelty}.
It is harder than classification as only positive samples of the class are available
rendering normal classification methods unusable.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novelty Detection}
\label{sec:novelty-detection}
% Introduce novelty detection
Novelty detection deals with detecting that a data sample belongs to a class
originated by a distribution other than the ones the system knows about~\cite{markou2003novelty}.
It is harder than classification as only positive samples of the class are available
rendering normal classification methods unusable.
